---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BVML

<!-- badges: start -->
<!-- badges: end -->

BVML is a patient stratification package for Bacteriosis Vaginalis disease. This package through a pre-trained Random Forest model and metagenomic profile of 8 bacterial species is able to classify patients into three classes:

- Class C1: patients with incipient dysbiosis.
- Class C2: patients with a BV+ profile.
- Class C3: patients with a BV- profile.

## Installation

To install the BVML, install from github using devtools:

``` r
install.packages("devtools")
library(devtools)
devtools::install_github("DiegoFE94/BVML")
```
## Functionalities

This section explains the different functionalities that constitute the package.

- convert_ncbi_ID: This function has as input a dataframe in which the columns correspond to the NCBI IDs of the 8 species and the rows to the samples. The function converts the NCBI IDs to the species names in the correct format for prediction.

- check_sps: This function has as input a dataframe whose columns correspond to the selected species and rows correspond to the samples. This function checks that all the required species are present in the dataframe and that they are in the correct format. Also try to put the species names in the required format.

- normdataset: This function has as input a dataframe whose columns correspond to the selected species and rows correspond to the samples. This function performs the log2 normalization of the species, a preprocessing necessary to perform the prediction.

- BVClassify: This function has as input a dataframe whose columns correspond to the selected species (in the correct format) and rows correspond to the samples. You can choose the type of input format of the species you are using by using the type (string) parameter. If you are using species names you should specify "species", however if you are using NCBI IDs you should specify "NCBI". It also has as input a logical value TRUE/FALSE. This function performs the classification of the samples into the three corresponding classes of the algorithm. The output is a dataframe where the columns correspond to the samples, the columns correspond to the probability of belonging to each class and to which class it corresponds according to the algorithm. In addition, if TRUE is selected in the input, it returns a Heatmap with the metagenomic profile of the dataframe.

## Example

This is a basic example which shows you how to use the package:

```{r example}
library(BVML)
# First charge a demo dataset
data(sample_data)
# Final step: make class prediction using species names and plotting the Heatmap
results <- BVClassify(sample_data, type = "species", plot_HM = TRUE)
```

## Questions? 
If you have any questions, please feel free to contact (diego.fedreira@udc.es).
