---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BVML

<!-- badges: start -->
<!-- badges: end -->

The goal of BVML is to classify patients from BV disease. The model in this package classifies patients into three classes:

- Class C1: patients with incipient dysbiosis
- Class C2: Patients with a BV+ profile.
- Class C3: patients presenting with a BV- profile

## Installation

To install the BVML, install from github using devtools:

``` r
install.packages("devtools")
library(devtools)
devtools::install_github("DiegoFE94/BVML")
```
## Example

This is a basic example which shows you how to use the package:

```{r example}
library(BVML)
# First charge a demo dataset
data(sample_data)
# Second step: check that we have all needed species and select them
s_data_checked <- check_sps(sample_data)
# Third step: normalise your data
norm_sample_data <- normdataset(s_data_checked)
# Final step: make class prediction
results <- BVClassify(norm_sample_data)

```
